%------------------------
% Author : Ben Walsh
% Github : https://github.com/benkwalsh
% "My CV"
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % remove all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjustment to margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-----------------------------------
% Custom setup
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Ben Walsh}} & Email: \href{mailto:}{ben.walsh4@icloud.com}\\
  \href{https://www.linkedin.com/in/ben-walsh-822558233/}{linkedin: linkedin.com/in/ben-walsh } & Mobile:~~~~~~~~~+64 027 415 8143 \\
  \href{https://github.com/benkwalsh}{Github: ~~github.com/benkwalsh} \\
\end{tabular*}

%-----------EDUCATION-----------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Canterbury}{Christchurch, New Zealand}
      {Bachelor of Science - Conjoint Major in Computer Science, Mathematics and Statistics}{Feb 2021 - Present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Concentrations:} Statistical Analysis, Programming, AI, Algorithms}}}
    \resumeSubheading
      {New Plymouth Boys High School}{New Plymouth, New Zealand}
      {NCEA Levels 1, 2, 3, Head of Niger House and School Prefect, Hostel Dux}{Feb 2016 - Dec 2020}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Concentrations:} Leadership, Academia, Sociability, Physical Health}}}
    \resumeSubHeadingListEnd

%----------PROFESSIONAL EXPERIENCE--------------

\vspace{-9pt}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{POSbiz Software Specialist}{Christchurch}
    {Student Specialist (Part-time)}{Feb 2023 - Present}
    \resumeItemListStart
        \resumeItem{Software}
          {Develop an exceptional understanding of the software.}
          \resumeItem{Communication}
          {Be able to articulate at a lower level how to use the software.}
          \resumeItem{Problem Solving}{Solve problems that customers have with the software quickly, and over the phone.}
      \resumeItemListEnd
    \resumeSubheading
		{University}{Christchurch}
		{Student (Full-time)}{Feb 2021 - Present}
		\resumeItemListStart
        \resumeItem{Statistical Analysis}
          {Multivariate Methods,  Regression Modelling, Computational Statistics}
        \resumeItem{Programming}
          {Formal Languages and Compilers, Graphing/Searching Algorithms (DP), R (Statistical Modelling)}
        \resumeItem{Mathematics}
          {Predominantly Statistics but also Discrete, Calculus, and Finance}
        \resumeItem{Engineering}
          {Product Design, Materials Science, Physics}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%----------LEADERSHIP EXPERIENCE--------------

\vspace{-5pt}
\section{Leadership Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Head of Niger House}{New Plymouth}
    {Student (Full-time)}{Feb 2020 - Dec 2020}
    \resumeItemListStart
        \item {Looked after 30, 17 year old men. This included ensuring daily chores were completed on time, problem solving and
        setting the example, all requiring exceptional people skills.}
        \vspace{-3pt}
        \item {Frequently talked in-front of 200 Hostel Students, laying down future plans and rule changes.}
        \vspace{-3pt}
        \item {Chairman for year group meetings, organising inter-hostel events.}
      \resumeItemListEnd
\vspace{-1pt}
    \resumeSubheading
	{School Prefect}{New Plymouth}
	{Student (Full-time)}{Feb 2020 - Dec 2020}
		\resumeItemListStart
        \item {Throughout the year I consistently read a Karakia and the daily notices to the whole school over the intercom system.}
        \vspace{-3pt}
        \item {Worked with an outside clothing business to design, calculate costs, manage, sell and market the leavers clothing/gear
        for 2020, this shown light on my managerial and organisation skills.}
        \vspace{-3pt}
        \item {In-forced school rules and disciplinary jobs on other wrong-doing students. Being stable with your new height \newline
        of power was important.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%---------VOLUNTEER EXPERIENCE------------

\vspace{-6pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Womens Refuge}{New Plymouth}
    {Philanthropist}{2018 - 2020}
    \resumeItemListStart
        \item {For 2 years in a row generated the largest amount of donations for the Women's Refuge during the annual New Plymouth 
        wide donation gathering.}
      \resumeItemListEnd
\vspace{-1pt}
    \resumeSubheading
	{Veterans Rest Home Care}{Christchurch}
	{Volunteer}{2021}
		\resumeItemListStart
        \item {Visited veterans on veterans day to enjoy some food and a chat. Was extremely fascinating and eye opening to hear their 
        thoughts on life and how they spent theirs.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS----------------

\vspace{-5pt}
\section{Skills/Interests/Miscellaneous}
\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, C, R, Latex}
	\resumeSubItem{Platforms/Tools}{Linux, Windows, Mac, Ubuntu, Microsoft Office, VScode, VIM, Rstudio, Adobe Photoshop}
	\resumeSubItem{Soft Skills}{Leadership, Public Speaking, Time Management}
    \resumeSubItem{Hobbies}{Golf, Skiing, Tech, Physical Health, Music}
\resumeSubHeadingListEnd

%-----------AWARDS-----------------

\vspace{-2pt}
\section{Honors and Awards}
\resumeSubHeadingListStart
    \item {Awarded Hostel DUX - November, 2020}
    \vspace{-5pt}
    \item {Mathematics and Statistics Honors (100\% in level 3 Statistics) - November 2020}
    \vspace{-5pt}
    \item {Ryder Memorial Award (Striking service with good humour, maintaining sound academic standards) - November, 2020}
\resumeSubHeadingListEnd

\end{document}
